\texorpdfstring{\ZpL}{ZpL}: a p-adic precision package

### 2018-05-07 ZpL/ZpL.tex
Working on referee comments

\noindent
\ZpXX is a generic notation for \ZpCR, \ZpLC and \ZpLF.
The first, \ZpCR, is the usual constructor for $p$-adic parents in 
\sage\footnote{It stands for \textit{capped relative}.}. It tracks 
precision using interval arithmetic. On the contrary
\ZpLC and \ZpLF are provided by our package. In the sequel, we will
compare the outputs provided by each parent.
As the results for \ZpLF and \ZpLC agree on all examples in this section, 
we shall only mention \ZpLC in the sequel.
More details about what are precisely \ZpLC and \ZpLF are provided in Section \ref{sec:implementation}.

In what follows, random elements in $\Zp$ are always picked with respect 
to the Haar measure. Random elements in $\Qp$ are constructed as a 
product $p^V \cdot U$ where $U$ is a random element in $\Zp$ 
(distributed according to the Haar measure) and $V$ is a random variable
taking values in $\Z$ which is independant from $U$ and distributed as
follows:
$$\textstyle
\text{Prob}[V{=}0] = \frac 1 5, \quad
\text{Prob}[V{=}v] = \frac 2 {5|v|\cdot (|v|+1)}, \, \forall v \neq 0.$$
This distribution is the default in \sage.

@@

We begin our tour of the features of the \ZpL package with some basic 
arithmetic computations.
We first pick some random element $x$.
The function {\color{function}\verb?random_element?} is designed so
that it guarantees that the picked random element is the same for
each constructor \ZpCR, \ZpLC and \ZpLF.

@@

\caption{Numbers of involved variables}
\label{fig:variables}
\end{figure}
%
The tables of Figure~\ref{fig:variables} show the total number of 
created variables (which reflects the complexity) together with the 
maximum number of variables alive at the same time (which reflects 
the memory occupation) while executing two basic computations.
The first one is the computation of the characteristic polynomial of a 
square matrix by the default algorithm used by \sage for $p$-adic fields 
(which is a division-free algorithm of quartic complexity) while the
second one is the computation of the gcd of two polynomials using a
naive Euclidean algorithm (of quadratic complexity). We can observe 
that, for both of them, the memory usage is roughly equal to the 
square root of the complexity.

@@

\noindent \textbf{Summary: Impact on complexity.}
% 
We consider the case of an algorithm with the following characteristics: 
its complexity is $c$ operations in $\Qp$ (without any tracking of 
precision), its memory usage is $m$ elements of $\Qp$, its input and its 
output have size $s_\inp$ and $s_\out$ (elements of $\Qp$) respectively.

>>>>

\noindent
\ZpXX is a generic notation for \ZpCR, \ZpLC and \ZpLF.
The first, \ZpCR, is the usual constructor for $p$-adic parents in 
\sage. It tracks 
precision using interval arithmetic. The parents 
\ZpLC and \ZpLF provided by our package\footnote{\text{\color{output} \rm \tt CR} stands for \textit{capped relative},
\text{\color{output} \rm \tt LC} for \textit{lattice-cap}, and \text{\color{output} \rm \tt LF} for \textit{lattice-float}.}
track precision differently; more details will be provided in Section \ref{sec:implementation}.
In the sequel, we will compare the outputs provided by each parent.
As the results for \ZpLF and \ZpLC agree on all examples in this section, 
we will only give those for \ZpLC.

In what follows, random elements in $\Zp$ are always picked with respect 
to the Haar measure. Random elements in $\Qp$ are constructed as a 
product $p^V \cdot U$ where $U$ is a random element in $\Zp$ 
(distributed according to the Haar measure) and $V$ is a random variable
taking values in $\Z$ which is independent from $U$ and distributed as
follows:
$$\textstyle
\text{Prob}[V{=}0] = \frac 1 5, \quad
\text{Prob}[V{=}v] = \frac 2 {5|v|\cdot (|v|+1)}, \, \forall v \neq 0.$$
This distribution is the default in \sage, and the function {\color{function}\verb?random_element?}
used below picks the same element for each of \ZpCR, \ZpLC and \ZpLF.

@@

We begin our tour of the \ZpL package with some basic 
arithmetic.  Elements are approximated by giving a valuation
and a unit, where the unit is specified modulo a power of $p$ determined
by the global lattice precision.

@@

\caption{Numbers of involved variables}
\label{fig:variables}
\end{figure}
%
The tables of Figure~\ref{fig:variables} show the total number of 
created variables (which reflects the complexity) together with the 
maximum number of variables alive at the same time (which reflects 
the memory usage) while executing two basic computations.
The first one is the computation of the characteristic polynomial of a 
square matrix by the default algorithm used by \sage for $p$-adic fields 
(which is a division-free algorithm of quartic complexity) while the
second one is the computation of the gcd of two polynomials using a
naive Euclidean algorithm (of quadratic complexity). We can observe 
that, for both of them, the memory usage is roughly equal to the 
square root of the complexity.

@@

\noindent \textbf{Summary: Impact on complexity.}
% 
We consider the case of an algorithm with the following characteristics: 
its complexity is $c$ operations in $\Qp$ (without any tracking of 
precision), its memory usage is $m$ elements of $\Qp$, its input and 
output have size $s_\inp$ and $s_\out$ (elements of $\Qp$) respectively.
